Trends of SDR in Thessaloniki

### 2023-06-06 Article.Rmd
Commit 2023-06-06 20:17

author:
  - name:        Natsis Athanasios
    email:       natsisphysicist@gmail.com
    affiliation: Laboratory of Atmospheric Physics
    correspondingauthor: true
    footnote:    1
  - name:        Alkiviadis Bais
    email:       bob@example.com
    affiliation: Another University
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  1 main street
    city:         Thessaloniki
    state:        State
    postcode:     123456
    country:      Greece
  - code:         Another University
    organization: Department
    addressline:  A street 29
    postcode:     2054 NX
    city:         Manchester,
    country:      The Netherlands
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.

@@

<!-- Seasonal -->
For the seasons of the year trends we grouped the mean daily values by season (December - February: Winter, March - May: Spring, etc.)

@@

This is it \@ref(fig:trendALL).

---------------------------

<!-- Deseasonalization -->
We remove the natural occurring seasonal variation, by calculating the mean
values for the corresponding time step, and subtracting them .........

>>>>

author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        bob@example.com
    affiliation:  Another University
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  1 main street
    city:         Thessaloniki
    state:        State
    postcode:     123456
    country:      Greece
  - code:         Another University
    organization: Department
    addressline:  A street 29
    postcode:     2054 NX
    city:         Manchester,
    country:      The Netherlands
footnote:
  - code:         1
    text:         "This is the first author footnote."
  - code:         2
    text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.

@@

<!-- Seasonal -->
For the seasons of the year trends, we also grouped the mean daily values by season (December - February: Winter, March - May: Spring, etc.)

<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation.
This is done, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
Thus, for each data set we have obtained the relative departure of the seasonal mean.
These values are presented in the following section.

.......................

filtering of means

statistical significance

Significance and aggregation scheme and filtering will be noted along with the corresponding results.

@@

About:

- long terms trends
- seasonal trends
- effect of SZA
- effect of clouds

- Aerosols
